# Working with Topol's health Study Wired
Loading summary function
```{r}
library(plyr)
library(rmarkdown)
```

Loading required packages


```{r}
library(dplyr)
library(psych)
library(ggplot2)
library(lme4)

```






First step is to look at data by describe function,drawing histograms,finding outliers, arranging in ascending/descending order(arrange function dplyr)
we plot the data also ggplot2, see factor in rlationship
we group data also describeBY,apply and tapply function
dplyr is important
selct,filter,rename,arrange,mutate,summarise functions important
reshape2 important in melting/recasting data
count and table functions important in 2 by 2 tables,x table , two dichotomous variables
Learn how to remove rows and columns
if median and mean are far off there are outliers can use subset or filter and select function to subset data(https://www.youtube.com/watch?v=ckxEZDN1iok)

```{r}
Topol <- read.csv("~/Desktop/Topol.csv")
describe(Topol)
describeBy(Topol$all_claims1,group = Topol$group)
describeBy(Topol$office_visits1,group = Topol$group)
t.test(Topol$all_claims1~Topol$group)
boxplot(Topol$all_claims1)
```
Arrange by descending order
```{r}
Topol1= arrange(Topol,desc(all_claims1))
```
Remove row 1 ,outlier
t test minus outlier
Data minus outlier
```{r}
Topol2 = Topol1[-1,]
t.test(Topol2$all_claims1~Topol2$group)
describe(Topol2$all_claims1)

str(Topol2)

#
t.test(Topol2$office_visits1~Topol2$group)

hist(Topol2$office_visits1)
# Poisson model
x = glm(Topol2$office_visits2~ Topol2$group , data = Topol2, family = poisson)
confint(x)
m = confint(x)
str(m)
m1 = as.data.frame(m)

# calculating exponential function to transform back

apply(m1,1,exp)

# Differnt way(http://www.sumsar.net/blog/2014/09/bayesian-first-aid-poisson-test/)
describeBy(Topol2$office_visits1,Topol2$group,)
?desc
# we want sum
tapply(Topol2$office_visits1,Topol2$group,FUN = sum)

# we will cdo Bayesian poisson t test, no. of visits in control = 305, Duration of time = 
count(Topol2$group)

 visits = c(305,309)
Duration = c(85,74) # person year


library(BayesianFirstAid)
bayes.poisson.test(visits, Duration, r = 1 ,alternative = "less")
bayes.poisson.test(visits, Duration, r = 1 ,alternative = "two.sided")
# Frequentist test

poisson.test(visits, Duration, r = 1 ,alternative = "two.sided")

plot(bayes.poisson.test(visits, Duration, r = 1 ,alternative = "two.sided"))


summarise(group_by(Topol2,group), m = sum(Topol2$office_visits1))

# Base R way sum
count(Topol2$group)
sum(Topol2$office_visits1[Topol2$group== "control"])

sum = Topol2 %>% select(Topol2$office_visits1)%>%filter(Topol2$group)

# without intercept
summary(glm(Topol2$office_visits2~ Topol2$group- 1, data = Topol2, family = poisson))
exp(1.28)
exp(1.44)
#
summarySE(data = Topol2,measurevar = Topol2$office_visits1,groupvars = Topol2$group)
describeBy(Topol2$office_visits1,group = Topol2$group)


```


